\theseminartitle \\ \small \thetitle

### 2021-09-28 tex/paper.tex
* Added data analysis python code * Minor additions to paper

	\begin{figure}[ht!]
		\centering
		\begin{subfigure}[b]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{outlier}
			\caption{Visualization of an outlier}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{changepoint}
			\caption{Visualization of a change point}
		\end{subfigure}
		\caption{Visual difference of an outlier and a change point}
		\label{fig:outlier_cp}
	\end{figure}

@@

	\begin{figure}[ht!]
		\centering
		\includegraphics[width=0.8\textwidth]{outlier}
		\caption{Compression- and Decompression speeds throughout the release history}
		\label{fig:release-bench}
	\end{figure}

@@

	\begin{figure}[ht!]
		\centering
		\includegraphics[width=0.8\textwidth]{outlier}
		\caption{Compression- and Decompression speeds throughout the release history of lz4hc}
		\label{fig:release-bench}
	\end{figure}

	Based on these results, it can be seen that there is a significant performance regression between versions \textit{v1.8.0} and \textit{v1.8.1}. Therefore this commit range was also selected for further investigation of the individual commits.

>>>>

	\begin{figure}[ht!]
		\centering
		\begin{subfigure}[b]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{graph/outlier}
			\caption{Visualization of an outlier}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{graph/changepoint}
			\caption{Visualization of a change point}
		\end{subfigure}
		\caption{Visual difference of an outlier and a change point}
		\label{fig:outlier_cp}
	\end{figure}

@@

	\begin{figure}[ht!]
		\centering
		\includegraphics[width=0.8\textwidth]{graph/lz4_releases_plot}
		\caption{Compression- and Decompression speeds throughout the release history}
		\label{fig:release-bench}
	\end{figure}

@@

	\begin{figure}[ht!]
		\centering
		\begin{subfigure}[b]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{graph/lz4hc_release_compression}
			\caption{Compression speed of \texttt{lz4hc} releases}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\textwidth}
			\centering
			\includegraphics[width=\textwidth]{graph/lz4hc_release_decompression}
			\caption{Decompression speed of \texttt{lz4hc} releases}
		\end{subfigure}
		\caption{Compression and Decompression speeds of \texttt{lz4hc} releases}
		\label{fig:release-bench-lz4hc}
	\end{figure}

	While the graph for the decompression speed is similar to the one for the normal \texttt{lz4} algorithm, for the compression speed a significant performance regression can be observed between versions \textit{v1.8.0} and \textit{v1.8.1}. Therefore this commit range was also selected for further investigation of the individual commits.
